A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-05-21 methodology.tex
large clusters

In our manual analysis, we randomly picked 50 datapoints of each cluster. If the cluster had fewer than 50 datapoints, we analyzed all of the datapoints in the cluster. Regarding general patterns, we obtained 577 clusters, out of which 428 included cross-project patterns. Of these 428 clusters, 35 clusters included more than 50 points. That is, we did not do random sampling for 393 clusters, we just manually analyzed all the datapoints in them. Regarding BC-related patterns, out of 102 obtained clusters, 49 clusters included cross-project patterns. Only 4 of these 49 clusters included more than 50 datapoints, therefore, we only did a random sampling for 4 clusters. For each cluster, we read the code and the bug reports of the datapoints (if they existed). If we judged that the members of a cluster fit into a pattern, we wrote a natural language description of that cluster. Considering the descriptions, we linked similar clusters together as possible candidates for merging. We considered these candidates and carried out appropriate ones. Finally, we selected 20 of the remaining clusters---the ones that manifested more-specific changes. Sections~\ref{sec:common_patterns}~and~\ref{sec:bc_patterns} present our clusters.

>>>>

For our manual analysis, we analyzed all datapoints in clusters with fewer than 50 datapoints, and randomly picked 50 datapoints from clusters with more than 50 datapoints. Such large clusters account for 35/428 cross-project general patterns (out of 577 general pattern clusters) and 4/49 BC-related patterns (out of 102 BC-related pattern clusters). We exhaustively analyzed all datapoints in the 393 small cross-project general patterns and 44 BC-related clusters.

For each cluster, we read the code and the bug reports of the datapoints (if they existed). If we judged that the members of a cluster fit into a pattern, we wrote a natural language description of that cluster. Considering the descriptions, we linked similar clusters together as possible candidates for merging. We considered these candidates and carried out appropriate ones. Finally, we selected 20 of the remaining clusters---the ones that manifested more-specific changes. Sections~\ref{sec:common_patterns}~and~\ref{sec:bc_patterns} present our clusters.
